\section{\label{sec:intro}Introduction}

\justifying
A cursory consideration of the technology we are using to define and deploy network infrastructure
reveals a declarative use of graphing as a descriptive language and in a definitive manner. Given this inherent
use of graphs, and a seemingly meteoric rise in the availability of Artificial Intelligence research and tooling, it feels
like a logical next step to transform these designs into a computationally suitable format. The use of Python, open
source modules, and the proliferation of scholarly papers and tutorials is a powerful combination indeed. As the common
refrain goes, gathering and making data suitable for analysis may be the largest challenge facing the would-be data
scientist.
\vspace{2mm}

\justifying
With these ideas in mind, this paper describes attempts to realize improvements in security and efficiency related to
automated deployment of network infrastructure by bringing powerful technology to bear on their source. Capturing attempts
to understand what's possible and find the edges of the problem space while learning new things is the true goal of this
work. Usable, useful or even interesting results are a happy accident. Using AI to uncover inferences, and realizing there are more,
better questions we can be asking is a mindset we can only cultivate by an undertaking like the one this paper describes.
\vspace{2mm}

\justifying
Where possible, code samples and screenshots of resultant execution are provided in an attempt to make the material
accessible to a greater number of readers. Studying and working in what is considered a sub-field of artificial
intelligence reveals a limited number of folks engaging in these methodologies. Mass market books on the field of
artificial intelligence are typically targeted towards helping folks get started in machine learning. While these books
are very interesting and educational, they don't get us far enough down the path of AI to help us with what seem to be
niche problems in deep learning (see figure \ref{aimldl}).
\vspace{2mm}

What graph neural network layering can we discover that will lead to useful features of the nodes?
Node classification for making predictions about the nodes.
Predictions on edges and their features.
Learning shared functions about nodes and edges to make predictions.
Is the regularity of security infrastructure (or perhaps certain sub-graphs) enough to realize solutions to inductive problems?

\justifying
Finally, the mathematics that underpin this effort, although off-putting for some, must be recognized and understood by
folks wishing to have questions answered with artificial intelligence. There is elegance and even beauty in this math.
\vspace{2mm}

\begin{displayquote}
	\emph{No human investigation can be called real science if it cannot be demonstrated mathematically.}
	- Leonardo Da Vinci
\end{displayquote}