\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{geometry}
\usepackage{hyperref}
\geometry{a4paper, margin=1in}

\title{Eternal Torment: Academic Reading List}
\author{Franklin Edward Diaz}
\date{\today}

\begin{document}

\maketitle

\section*{Overview}
This document maintains a curated list of literature and technical manuals that inform the algorithmic and mathematical implementations within the \texttt{eternal-torment} repository.

\section{Core Mathematics}

\subsection*{Discrete Mathematics with Ducks}
\textbf{Author:} dr. sarah-marie belcastro \\
\textbf{Status:} Active Study / Research Phase

\subsubsection*{Summary}
This text provides a discovery-based approach to discrete mathematics, emphasizing intuition and formal proof through accessible themes. It serves as the primary theoretical framework for the repository's cryptographic and algorithmic suites.

\subsubsection*{Relevant Themes \& Repository Mapping}
\begin{itemize}
    \item \textbf{Theme I: Logic and Proofs} --- Applied to the \texttt{FIZZBUZZ/} polyglot suite as a study in \textit{Proof by Cases} and \textit{Exhaustive Induction}.
    \item \textbf{Theme II: Number Theory and Cryptography} --- Directly informs the \texttt{vigenere/}, \texttt{trithemius/}, and \texttt{rail-fence/} implementations. Focuses on modular arithmetic ($a \equiv b \pmod{n}$) and shift transformations.
    \item \textbf{Theme III: Graph Theory} --- Theoretical backing for the \texttt{palm-api/} Graphviz visualizations and future cluster network topology mappings.
    \item \textbf{Theme IV: Combinatorics} --- Utilized for analyzing the time and space complexity ($O$-notation) of transposition and substitution ciphers.
\end{itemize}

\section{Low-Level \& Systems}

\subsection*{ARM Assembly Language: Fundamentals and Techniques}
\textbf{Focus:} AArch64 instruction sets for the NVIDIA Jetson Nano architecture. 
\textbf{Application:} Core logic for \texttt{src/ass/} and hardware-level performance optimization.

\section{Machine Learning}

\subsection*{Hands-On Machine Learning with Scikit-Learn, Keras, and TensorFlow}
\textbf{Application:} Configuring the \texttt{src/tensorflow/} directory, specifically managing \texttt{set\_memory\_growth} for the shared memory architecture of the 2GB DevKit.

\section{Recommended for Future Study}

\subsection*{Gödel, Escher, Bach: An Eternal Golden Braid}
\textbf{Author:} Douglas Hofstadter \\
\textbf{Focus:} Formal systems, recursion, and self-reference. Essential for deep logic and AI theory.

\subsection*{Things to Make and Do in the Fourth Dimension}
\textbf{Author:} Matt Parker \\
\textbf{Focus:} Recreational mathematics and geometric visualization. Useful for \texttt{src/graphics/} experimentation.

\subsection*{How Not to Be Wrong}
\textbf{Author:} Jordan Ellenberg \\
\textbf{Focus:} Mathematical logic and its application to societal structures.

\end